Manuscript

### 2019-01-16 manuscript.Rmd
updated papaja doc and made new venn diagrams

> **(???) Trametinib and selumetinib are both *MEK* inhibitors, and pazopanib is a *VEGFR* inhibitor. VEGF signaling can influence the MAPK/ERK signaling pathway, which promotes cell proliferation and survival. This pathway includes *RAS*, *BRAF*, and *MEK* proteins. These results underscore the importance of the MAPK/ERK signaling pathway in cancer.**

However, taking these results as a whole, we observe little concordance between G2P associations and the correlation of mutation status and AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets. This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response. We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...

```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("./plots/manuscript/drugscreen_venn.png")
```

> **(???) Cut this analysis since we are comparing distributions of p-values?**

@@

```{r ksplot, echo = FALSE, warning = FALSE, message = FALSE, fig.cap="Comparison of Spearman correlation coefficients derived from copy number (log$_2$ ratio), gene expression (RPKM), and AUC z-scores from G2P drug-gene associations. Coefficients were grouped by whether or not the associated lineage for each comparison was in a G2P drug-gene-lineage association or not. Distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests."}
knitr::include_graphics("./plots/manuscript/g2p_spearman_ks_res_plot.png")
```

@@

```{r crispr-venn, echo = FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("./plots/manuscript/crispr_venn.png")
```

>>>>

> **(???) Trametinib and selumetinib are both *MEK* inhibitors, and pazopanib is a *VEGFR* inhibitor. VEGF signaling can influence the MAPK/ERK signaling pathway, which promotes cell proliferation and survival. This pathway includes *RAS*, *BRAF*, and *MEK* proteins.**

However, taking these results as a whole, we observe little concordance between G2P associations and the correlation of mutation status and AUC for said G2P association, suggesting that mutation status alone is not a robust predictor of clinically actionable genetic targets. This led us to examine the correlations between AUC and gene expression and AUC and copy number, two other genomic features that are known to associate with cancer and drug response. We computed Spearman correlation coefficients ($r_s$) between AUC of each drug-gene association and gene expression (RPKM) and copy number (log$_2$ ratio) of the gene in the association...**(???) need to complete this thought/analysis**

(ref:drug-venn) Overlap of drug-gene associations drawn from all pairwise combinations of G2P drugs and G2P genes whose drug effects significantly correlated with (**A**) mutation status, (**B**) gene expression, and (**C**) copy number across CCLE, CTRP, and GDSC.

```{r drug-venn, echo = FALSE, message=FALSE, warning=FALSE, fig.cap='(ref:drug-venn)'}
knitr::include_graphics("./plots/manuscript/drugscreen_venns.pdf")
```

> **(???) Cut these next three paragraphs since we cut the analysis, but keep for future reference**

@@

(ref:ksplot) Comparison of Spearman correlation coefficients ($r_s$) derived from copy number (log$_2$ ratio), gene expression (RPKM), and AUC z-scores from G2P drug-gene associations. Coefficients were grouped by whether or not the associated lineage for each comparison was in a G2P drug-gene-lineage association or not. Distributions of these grouped coefficients were compared using Kolmogorov-Smirnov tests.

```{r ksplot, echo = FALSE, warning = FALSE, message = FALSE, fig.cap='(ref:ksplot)'}
knitr::include_graphics("./plots/manuscript/g2p_spearman_ks_res_plot.pdf")
```

@@

(ref:crispr-venn) Overlap of genes whose gene expression and/or copy number significantly correlated with CERES score.

```{r crispr-venn, echo = FALSE, message=FALSE, warning=FALSE, fig.cap='(ref:crispr-venn)'}
knitr::include_graphics("./plots/manuscript/crispr_venn.pdf")
```
